\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2014-10-25 doc/flexiblesusy-paper.tex

\fs already comes with plenty of predefined models: the CMSSM (simply
called \code{MSSM}), the NMSSM in it's $Z_3$-symmetric form (called \code{NMSSM}), $Z_3$-violating NMSSM (\code{SMSSM}), the USSM (\code{UMSSM}),
the NUHM \ESSM (\code{E6SSM}) \cite{Athron:2007en}, the
right-handed neutrino extended MSSM (\code{MSSMRHN}), the NUHM-MSSM
(\code{NUHMSSM}) and the $R$-symmetric MSSM (\code{MRSSM})
\cite{Kribs:2007ac}.  See the content of \code{model_files/} for all
predefined model files.  For all these models spectrum generators can
be generated easily like for the CMSSM in
\secref{sec:quick-start-cmssm}.  The spectrum generator for the
$Z_3$-symmetric NMSSM for example can be generated like this:
%
\begin{lstlisting}[language=bash]
$ ./createmodel --name=NMSSM
$ ./configure --with-models=NMSSM
$ make
\end{lstlisting}%% $
%
One of the design goals is modularity and the possibility to easily
construct custom spectrum generators.  The details of the
customization can be found in Sections
\ref{sec:modfile}--\ref{sec:Flexible}.  As a simple example consider
the NMSSM.  The NMSSM variant above unifies all soft-breaking
trilinear scalar couplings at the GUT scale.  In order to relax this
constraint and use a separate value for $A_\lambda$ at the GUT scale
one can edit the model file \code{model_files/NMSSM/FlexibleSUSY.m.in} and
change the lines
%
\begin{lstlisting}[language=Mathematica]
EXTPAR = { {61, LambdaInput} };

>>>>

\fs already comes with plenty of predefined models: the CMSSM (simply
called \code{MSSM}), the NMSSM in its $Z_3$-symmetric form (called \code{NMSSM}), $Z_3$-violating NMSSM (\code{SMSSM}), the USSM (\code{UMSSM}),
the NUHM \ESSM (\code{E6SSM}) \cite{Athron:2007en}, the
right-handed neutrino extended MSSM (\code{MSSMRHN}), the NUHM-MSSM
(\code{NUHMSSM}) and the $R$-symmetric MSSM (\code{MRSSM})
\cite{Kribs:2007ac}.  See the content of \code{model_files/} for all
predefined model files.  For all these models spectrum generators can
be generated easily like for the CMSSM in
\secref{sec:quick-start-cmssm}.  The spectrum generator for the
$Z_3$-symmetric NMSSM for example can be generated like this:
%
\begin{lstlisting}[language=bash]
$ ./createmodel --name=NMSSM
$ ./configure --with-models=NMSSM
$ make
\end{lstlisting}%% $
%
One of the design goals is modularity and the possibility to easily
construct custom spectrum generators.  The details of the
customization can be found in Sections
\ref{sec:modfile}--\ref{sec:Flexible}.  As a simple example consider
the NMSSM.  The NMSSM variant above unifies all soft-breaking
trilinear scalar couplings at the GUT scale.  In order to relax this
constraint and use a separate value for $A_\lambda$ at the GUT scale
one can edit the model file \code{model_files/NMSSM/FlexibleSUSY.m.in} and
change the lines
%
\begin{lstlisting}[language=Mathematica]
EXTPAR = { {61, LambdaInput} };
